Measurement Bias from Address Aliasing

### 2016-05-25 presentation.tex
Clean up counter info

  \begin{itemize}
    \item Older architectures, such as Core, have alias covered in a more general event:
  \end{itemize}

  \begin{description}
    \item[{\small LOAD\_BLOCKS.OVERLAP\_STORE.}] 
    \emph{``Loads that partially overlap an earlier store, or 4-Kbyte aliased with a previous store.''} 
    \cite[Table 19-17]{Volume3B}
  \end{description}

@@

\begin{itemize}
  \item Mark buffers with \texttt{restrict}.
  \begin{itemize}
    \item Can allow the optimizer to reduce number of memory accesses.
  \end{itemize}
  \item Use a special purpose allocator.
  \begin{itemize}
    \item Heuristics for avoiding pairwise aliasing buffers.
    \item No known implementation with this goal in mind, to our knowledge.
  \end{itemize}
  \item Manually adjust address offset.
  \begin{itemize}
    \item Consider memory address alignment for performance tuning inner loops.
    \item Auto-tuning?
  \end{itemize}
\end{itemize}

>>>>

  Same or similar counters found in architectures dating back through Core 2.

  % \begin{itemize}
  %   \item Older architectures, such as Core, have alias covered in a more general event:
  % \end{itemize}

  % \begin{description}
  %   \item[{\small LOAD\_BLOCKS.OVERLAP\_STORE.}] 
  %   \emph{``Loads that partially overlap an earlier store, or 4-Kbyte aliased with a previous store.''} 
  %   \cite[Table 19-17]{Volume3B}
  % \end{description}

@@

\begin{itemize}
  \item Mark buffers with \texttt{restrict}.
  \begin{itemize}
    \item Can allow the optimizer to reduce number of memory accesses.
  \end{itemize}
  \item Use a special purpose allocator.
  \begin{itemize}
    \item Heuristics for avoiding pairwise aliasing buffers.
    \item No known implementation with this goal in mind, to our knowledge.
  \end{itemize}
  \item Explicitly adjust address offset.
  \begin{itemize}
    \item Consider memory address alignment for performance tuning inner loops.
    \item Buffer addresses as candidate for automatic performance tuning
  \end{itemize}
\end{itemize}
